Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-08-30 ms/main.tex
draft for abstract

% Abstract
%\begin{abstract}
%\end{abstract}

>>>>

% Abstract
\begin{abstract}
We construct models for the cultural evolution of cooperation in a well-mixed population with vertical, horizontal, and oblique transmission. Conditions are found for fixation of cooperation, fixation of defection, and stable coexistence between cooperation and defection, and comparisons are drawn with Hamilton's rule. A spatial model is constructed and its results are compared to the well-mixed model.
We show that assortment between cooperation and horizontal transmission facilitates the evolution of cooperation and increases the population mean fitness. 
% TODO what about oblique?
\end{abstract}
